VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_arch.tex
re

\subsection{Per Node Software Components} 
%\begin{figure}[htbp]
\begin{figure}[htbp]
\vspace{1em}
    \centering
    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
    \includegraphics[width=3in]{images/socc_arch_cluster}
%\vspace{1em}
    \caption{Data flow during snapshot backup}
    \label{fig:arch_vm}
\end{figure}
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

%\begin{figure}[htbp]
\begin{figure}[htbp]
\vspace{1em}
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=3in]{images/sstore_arch}
%\vspace{1em}
  \centering
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
a set of data chunks and is the basic unit in data access and retrieval. 
In writing a chunk during backup, the system accumulates data chunks and stores the entire
group as a unit after compression. This  compression can reduce data by several times  in our tested data.
When accessing a particular chunk, its chunk group is retrieved from the storage
and decompressed. Given the high spatial locality and usefulness of prefetching  in 
snapshot chunk accessing~\cite{Guo2011,foundation08},
retrieval of  a data chunk  group naturally works well with prefetching. 
A  typical chunk group contains 1000 chunks in our experiment.
% with an average size of 200-600 chunks.

>>>>

\subsection{Per Node Software Components} 
%\begin{figure}[htbp]
\begin{figure}[htbp]
%\vspace{1em}
    \centering
    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
    \includegraphics[width=3in]{images/socc_arch_cluster}
%\vspace{1em}
    \caption{Data flow during snapshot backup}
    \label{fig:arch_vm}
\end{figure}
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

%\begin{figure}[htbp]
\begin{figure}[htbp]
%\vspace{1em}
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=3in]{images/sstore_arch}
%\vspace{1em}
  \centering
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

Each non-PDS data container is further divided into a set of chunk data groups. Each chunk group is composed of
a set of data chunks and is the basic unit in data access and retrieval. 
In writing a chunk during backup, the system accumulates data chunks and stores the entire
group as a unit after compression. This  compression can reduce data by several times  in our tested data.
When accessing a particular chunk, its chunk group is retrieved from the storage
and decompressed. Given the high spatial locality and usefulness of prefetching  in 
snapshot chunk accessing~\cite{Guo2011,Rhea2008},
retrieval of  a data chunk  group naturally works well with prefetching. 
A  typical chunk group contains 1000 chunks in our experiment.
% with an average size of 200-600 chunks.
